Localisation and Sensor Privacy Using the Extended Information Filter and Private Linear-Combination Aggregation\thanksref{footnoteinfo}

### 2020-09-01 main.tex
Added encoding section, in more detail than in the past. Changes definition and remark environments to use correct ones from the scheme Added armin and argmax definitions

\theoremstyle{definition}
\newtheorem{definition}{Definition}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

@@

\subsection{Security Notions}
The security of a cryptographic scheme is typically defined by a security \textit{game}, which captures both the desired privacy guarantees, as well as the capabilities of attackers \cite{katzIntroductionModernCryptography2008}. The typical security notion for a homomorphic encryption scheme is Indistinguishability under Chosen Plaintext Attack (IND-CPA) \cite{chaseSecurityHomomorphicEncryption2017}. 
\begin{definition}
An encryption scheme meets IND-CPA security if an attacker who can choose plaintext messages to be encrypted at will, gains no additional information about an unknown plaintext message when they learn only its encryption.

The formal security game for IND-CPA has been given in Appendix \ref{app:ind_cpa}.
\end{definition}
Private aggregation schemes aim for the security notion of Aggregator Obliviousness (AO) \cite{shiPrivacyPreservingAggregationTimeSeries2011}. 
\begin{definition}
An encryption scheme meets AO security if no colluding subset of participants \textit{excluding} the aggregator gains additional information about the remaining aggregation values given only their encryptions, while any colluding subset \textit{including} the aggregator learns only their sum.

The formal security game for AO has been given in Appendix \ref{app:ao}.
\end{definition}

@@

\begin{remark}
    The notion of a leakage function including parameters from the aggregator requires extra care to be taken when giving its definition. Since an attacker may compromise the aggregator, they have control over the choice of these parameters, and therefore over the leakage function. We note that in the leakage function above, $\sum^n_{i=n}\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by the colluding subset, \textit{e.g.} $\sum^m_{j=1}x^{(t)}_{1,j}$ given weights $(1,0,\dots,0)$, but that individual sensor values $x^{(t)}_{i,j}$ remain private due to the requirement that all sensors receive the same weights.
\end{remark}

@@

\begin{definition}
    An encryption scheme meets LCAO security if no adversary, running in probabilistic-time with respect to security parameter, has more than a negligible advantage in winning the above security game. Probabilities are taken over randomness introduced by $\mathcal{A}$, and in $\mathsf{Setup}$, $\mathsf{Enc}$ and $\mathsf{CombEnc}$.
\end{definition}

@@

    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\dots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$] The linear combination encryption step at time $t$ is computed as 
    \begin{equation}
        y^{(t)}_i = H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2}\,,
    \end{equation}
    and makes use of the homomorphic property \eqref{eqn:paillier_hom_mult}. Correctness follows from
    \begin{equation*}
        \begin{split}
             y^{(t)}_i &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2} \\
            &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(x^{(t)}_{i,j}\omega^{(t)}_j) \pmod{N^2} \\
            &= H(t)^{sk_i}\prod^{m}_{j=1}(N+1)^{x^{(t)}_{i,j}\omega^{(t)}_j} r^{N}_{j} \pmod{N^2} \\
            &= H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j} r_{i}^{N} \pmod{N^2}\,,
        \end{split}
    \end{equation*}
    for some values $r_i,r_j \in \mathbb{Z}_N\,,1\leq j \leq m$. Here, $r_i^N$ and $H(t)^{sk_i}$ can be considered the noise terms corresponding to the two levels of encryption from $pk_0$ and $sk_i$, respectively.

@@

\section{Private Localisation Preliminaries}
The localisation filter we introduce requires real-valued inputs and functions, and relies on a non-linear measurement model. We make use of an existing real-number encoding scheme which supports the homomorphic operations we'll require and an algebraic reformulation of the Extended Kalman Filter which reduces the filter update step to only use these operations.

@@

In the encryption scheme introduced, weights and values are limited to integer values, and operations computed $\pmod{N}$ bound meaningful inputs to $x \in \mathbb{Z}_N$ for any weight or value $x$. The encoding scheme we have used

The encoding scheme is defined by the quantisation parameter $f$, representing the number of bits used to quantise the fractional part of a real number, and $N$ the modulus to use for handling negative numbers.

Encoding of a real number $a \in \mathbb{R}$ to an integer $e \in \mathbb{Z}$ is computed by
\begin{equation}
    e = \left\lfloor 2^{(m+1)f} a \right\rceil \pmod{N}\,,
\end{equation}
and decoding after $m$ homomorphic multiplications is computed by
\begin{equation}
    a = 
    \begin{dcases}
        \frac{e\hspace{-7pt}\pmod{N}}{2^{(m+1)f}}, &e\hspace{-7pt}\pmod{N} \leq \left\lfloor\frac{N}{2}\right\rfloor \\
        -\frac{N - e\hspace{-7pt}\pmod{N}}{2^{(m+1)f}}, &e\hspace{-7pt}\pmod{N} > \left\lfloor\frac{N}{2}\right\rfloor \\
    \end{dcases}\,.
\end{equation}

Note that adding encoding number to already encoded number requires the number of multiplications to be matched

that for the largest number of multiplications $m$, parameters for the encoding scheme when used with our ecncryption scheme should be defined such that
\begin{equation*}
    something \leq something\,else
\end{equation*}

encodings grow in size exponentially for each multilpication.

>>>>

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

\subsection{Security Notions}
The security of a cryptographic scheme is typically defined by a security \textit{game}, which captures both the desired privacy guarantees, as well as the capabilities of attackers \cite{katzIntroductionModernCryptography2008}. The typical security notion for a homomorphic encryption scheme is Indistinguishability under Chosen Plaintext Attack (IND-CPA) \cite{chaseSecurityHomomorphicEncryption2017}. 
\begin{defn}
An encryption scheme meets IND-CPA security if an attacker who can choose plaintext messages to be encrypted at will, gains no additional information about an unknown plaintext message when they learn only its encryption.

The formal security game for IND-CPA has been given in Appendix \ref{app:ind_cpa}.
\end{defn}
Private aggregation schemes aim for the security notion of Aggregator Obliviousness (AO) \cite{shiPrivacyPreservingAggregationTimeSeries2011}. 
\begin{defn}
An encryption scheme meets AO security if no colluding subset of participants \textit{excluding} the aggregator gains additional information about the remaining aggregation values given only their encryptions, while any colluding subset \textit{including} the aggregator learns only their sum.

The formal security game for AO has been given in Appendix \ref{app:ao}.
\end{defn}

@@

\begin{rem}
    The notion of a leakage function including parameters from the aggregator requires extra care to be taken when giving its definition. Since an attacker may compromise the aggregator, they have control over the choice of these parameters, and therefore over the leakage function. We note that in the leakage function above, $\sum^n_{i=n}\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by the colluding subset, \textit{e.g.} $\sum^m_{j=1}x^{(t)}_{1,j}$ given weights $(1,0,\dots,0)$, but that individual sensor values $x^{(t)}_{i,j}$ remain private due to the requirement that all sensors receive the same weights.
\end{rem}

@@

\begin{defn}
    An encryption scheme meets LCAO security if no adversary, running in probabilistic-time with respect to security parameter, has more than a negligible advantage in winning the above security game. Probabilities are taken over randomness introduced by $\mathcal{A}$, and in $\mathsf{Setup}$, $\mathsf{Enc}$ and $\mathsf{CombEnc}$.
\end{defn}

@@

    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\dots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$] The linear combination encryption step at time $t$ is computed as 
    \begin{equation}
        y^{(t)}_i = H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2}\,,\label{eqn:our_scheme_lin_comb}
    \end{equation}
    and makes use of the homomorphic property \eqref{eqn:paillier_hom_mult}. Correctness follows from
    \begin{equation*}
        \begin{split}
             y^{(t)}_i &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2} \\
            &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(x^{(t)}_{i,j}\omega^{(t)}_j) \pmod{N^2} \\
            &= H(t)^{sk_i}\prod^{m}_{j=1}(N+1)^{x^{(t)}_{i,j}\omega^{(t)}_j} r^{N}_{j} \pmod{N^2} \\
            &= H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j} r_{i}^{N} \pmod{N^2}\,,
        \end{split}
    \end{equation*}
    for some values $r_i,r_j \in \mathbb{Z}_N\,,1\leq j \leq m$. Here, $r_i^N$ and $H(t)^{sk_i}$ can be considered the noise terms corresponding to the two levels of encryption from $pk_0$ and $sk_i$, respectively.

@@

\section{Private Localisation Preliminaries}
The localisation filter we introduce requires real-valued inputs and functions, and relies on a non-linear measurement model. We make use of a real-number encoding scheme which supports the required homomorphic operations and an algebraic reformulation of the Extended Kalman Filter which reduces the filter update step to use only these operations.

@@

In the encryption scheme introduced, weights and values are restricted to integers and all operations are computed $\pmod{N}$, thus bounding meaningful inputs to $\{x : x \in \mathbb{Z}_N\}$. For this reason, a quantisation and integer mapping method for real numbers is required for their encryption and homomorphic processing. We quantise with a generalised Q number format \cite{oberstarFixedPointRepresentationFractional2007} due to implementation simplicity and applicability.

We define a subset of rational numbers in terms of a range $r \in \mathbb{N}$ and fractional precision $f \in \mathbb{N}$. This contrasts with the common definition given in terms of total bits $a$ and fractional bits $b$ \cite{oberstarFixedPointRepresentationFractional2007,schulzedarupEncryptedCooperativeControl2019,farokhiSecurePrivateControl2017}, but allows for a direct mapping to integer ranges which are not powers of two. Rational subset $\mathbb{Q}_{r,f}$ is given by
\begin{equation*}
    \mathbb{Q}_{r,f} = \left\{q : f^{-1} | q \wedge -\left\lfloor\frac{r}{2}\right\rfloor \leq q < \left\lfloor\frac{r}{2}\right\rfloor \right\}\,,
\end{equation*}
and we quantise any real number $x$ by taking the nearest rational $q \in \mathbb{Q}_{r,f}$. That is, $\argmin_{q\in\mathbb{Q}_{r,f}} |x-q|$. In this form, mapping rationals $\mathbb{Q}_{r,f}$ to the encryption scheme range $\mathbb{Z}_N$ is achieved by choosing $r=N$, and handling negatives with modulo arithmetic. In addition, we note that the Q number format requires a precision factor $f$ to be removed after each encoded multiplication, which is not supported by our encryption scheme. This is captured by a third parameter $m$; the number of \textit{additional} multiplication factors to add or remove from encodings.

The combined quantisation and encoding function $\mathsf{E}_{r,f,m}(x)$ of a given a real number $x \in \mathbb{R}$, integer range $\mathbb{Z}_N$, and the desired scaling for $m$ prior encoded multiplications, is given by
\begin{equation}
    \mathsf{E}_{N,f,m}(x) = \left\lfloor f^{m+1} x \right\rceil \pmod{N}\,. \label{eqn:encode}
\end{equation}
Decoding of integer $e \in \mathbb{Z}_N$, is given by
\begin{equation}
    \mathsf{E}^{-1}_{N,f,m}(e) \!=\! 
    \begin{dcases}
        \frac{e\hspace{-8pt}\pmod{N}}{f^{m+1}}, &e\hspace{-8pt}\pmod{N} \leq \left\lfloor\frac{N}{2}\right\rfloor \\
        -\frac{N - e\hspace{-8pt}\pmod{N}}{f^{m+1}}, &\text{otherwise} \\
    \end{dcases}.
\end{equation}

This encoding scheme provides the following homomorphic operations,
\begin{equation}
    \begin{split}
        \mathsf{E}_{N,f,m}(a_1) + \mathsf{E}_{N,f,m}(a_2)& \pmod{N} =\\
        &\mathsf{E}_{N,f,m}(a_1+a_2)
    \end{split}
\end{equation}
and
\begin{equation}
    \begin{split}
        \mathsf{E}_{N,f,m}(a_1)\mathsf{E}_{N,f,m}(a_2)& \pmod{N} =\\
        &\mathsf{E}_{N,f,m+1}(a_1a_2)\,,
    \end{split}
\end{equation}
noting that the modulus corresponds with the encrypted homomorphic operations in \eqref{eqn:our_scheme_lin_comb}.

The choice of a high fractional precision $f$ may reduce quantisation erros introduced in \eqref{eqn:encode}, however, risks an overflow following too many multiplications. Given the largest number of expected multiplications $m_{max}$, and the largest expected decoded value $x$, the parameter should be chosen such that the following condition holds
\begin{equation*}
    \left|f^{m_{max}+1}x\right| < \left\lfloor \frac{N}{2} \right\rfloor\,.
\end{equation*}
In practice, $N$ is typicaly very large ($N>2^{1024}$) and this condition can be ignored.
